D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-04 ootavacuous.tex
Add JMM Causality Test Cases 9 and 9a
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

>>>>

\subsubsection{Causality Test Case 9}
\label{app:Causality Test Case 9}

Listing~\ref{lst:Causality Test Case 9}
shows causality test case 9, for which the \co{r1 == r2 == 1}
result is to be allowed.
The herd7 tool does not find this cycle, but when \co{r2} is explicitly
initialized to the constant \co{1}, it does find the cycle and refrains
from flagging it as an OOTA cycle.

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-9.litmus @@
\end{verbatim}
\caption{Causality Test Case 9}
\label{lst:Causality Test Case 9}
\end{listing}

\subsubsection{Causality Test Case 9a}
\label{app:Causality Test Case 9a}

Listing~\ref{lst:Causality Test Case 9a}
shows causality test case 9a, for which the \co{r1 == r2 == 1}
result is to be allowed.
The herd7 tool does not find this cycle, but when \co{r2} is explicitly
initialized to the constant \co{1}, it does find the cycle and refrains
from flagging it as an OOTA cycle.

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-9a.litmus @@
\end{verbatim}
\caption{Causality Test Case 9a}
\label{lst:Causality Test Case 9a}
\end{listing}
